The impact of cosmic variance on simulating weak lensing surveys

### 2014-12-01 Writeup/paper_v3.tex
Viola et al

 \rachel{Some types of information about and tests of shear estimation
   for ongoing and future weak lensing surveys will rely on data from
   the Hubble Space Telescope ({\em HST}).  For example, data from
   {\em HST} can be used to derive basic statistics of galaxy light
   profiles, such as joint distributions of size and the morphology.
   It can be used to infer the intrinsic distribution of galaxy
   shapes, which enters the shear estimation process either implicitly
 or explicitly depending on the method used for shear estimation.
 Going beyond basic information about the light profile, {\em HST} can
be used to quantify the detailed morphology of galaxies, due to its
higher resolution compared to any current or planned weak lensing
survey.  Finally, it can be used to address systematics due to colour
gradients within galaxies, which are particularly problematic when
combined with a wavelength-dependent diffraction-limited PSF
\citep[e.g.,][]{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.}

@@

\rachel{However, once the Euclid survey is
  underway, the derivation of simple galaxy morphology and the
  intrinsic ellipticity distribution will be based on the 40~deg$^2$
  Euclid deep field, which goes two magnitudes fainter than the rest of
  the survey.  With that data in hand, the Euclid weak lensing
  results will be less reliant on the much smaller and more
  cosmic variance-limited {\em HST} fields, using them only for colour
  gradient calibration and estimates of the impact of detailed galaxy
  morphology (since the {\em HST} resolution is higher than that
  of Euclid).}

>>>>

 \rachel{Some types of information about and tests of shear estimation
   for ongoing and future weak lensing surveys will rely on data from
   the Hubble Space Telescope ({\em HST}).  For example, data from
   {\em HST} can be used to derive basic statistics of galaxy light
   profiles, such as joint distributions of size and the morphology.
   It can be used to infer the intrinsic distribution of galaxy
   shapes, which enters the shear estimation process either implicitly
 or explicitly depending on the method used for shear estimation
 \citep[see, e.g.,][]{2014MNRAS.439.1909V}.
 Going beyond basic information about the light profile, {\em HST} can
be used to quantify the detailed morphology of galaxies, due to its
higher resolution compared to any current or planned weak lensing
survey.  Finally, it can be used to address systematics due to colour
gradients within galaxies, which are particularly problematic when
combined with a wavelength-dependent diffraction-limited PSF
\citep[e.g.,][]{2012MNRAS.421.1385V,2013MNRAS.432.2385S}.}

@@

\rachel{However, once the Euclid survey is
  underway, the derivation of simple galaxy morphology and the
  intrinsic ellipticity distribution will be based on the 40~deg$^2$
  Euclid deep field, which goes two magnitudes fainter than the rest of
  the survey.  With that data in hand, the Euclid weak lensing
  results will be less reliant on the much smaller and more
  cosmic variance-limited {\em HST} fields, using them only for colour
  gradient calibration and estimates of the impact of detailed galaxy
  morphology (since the {\em HST} resolution is higher than that
  of Euclid).  The findings of \cite{2014MNRAS.439.1909V} demonstrate that the area of
  this deep field is sufficient to accomplish the goal of determining
  the intrinsic ellipticity distribution at the accuracy required for
  shear calibration purposes for the Euclid survey.}
